### 2025-04-16 multiple-regression.qmd
20250415 - fixes

The variable shows a strong positive skew.
To address a strong positive skew, we can use a log transformation.
The histogram of the log-transformed variable is in @fig-histogramTargetSharesLog.

@@

```{r}
mediationFit <- sem(
  mediationModel,
  data = player_stats_seasonal,
  se = "bootstrap",
  bootstrap = 1000, # generally use 10,000 bootstrap draws; this example uses 1,000 for speed
  parallel = "multicore", # parallelization for speed: use "multicore" for Mac/Linux; "snow" for PC
  iseed = 52242, # for reproducibility
  missing = "ML",
  estimator = "ML",
  std.lv = TRUE,
  fixed.x = FALSE)
```

@@

```{r}
multipleMediatorFit <- sem(
  multipleMediatorModel,
  data = player_stats_seasonal,
  se = "bootstrap",
  bootstrap = 1000, # generally use 10,000 bootstrap draws; this example uses 1,000 for speed
  parallel = "multicore", # parallelization for speed: use "multicore" for Mac/Linux; "snow" for PC
  iseed = 52242, # for reproducibility
  missing = "ML",
  estimator = "ML",
  std.lv = TRUE,
  fixed.x = FALSE)
```

>>>>

The variable shows a strong positive skew.
To address a strong positive skew, we can use a log transformation.
The histogram of the log-transformed variable is in @fig-histogramTargetSharesTransformed.

@@

```{r}
mediationFit <- sem(
  mediationModel,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  se = "bootstrap",
  bootstrap = 1000, # generally use 10,000 bootstrap draws; this example uses 1,000 for speed
  parallel = "multicore", # parallelization for speed: use "multicore" for Mac/Linux; "snow" for PC
  iseed = 52242, # for reproducibility
  missing = "ML",
  estimator = "ML",
  fixed.x = FALSE)
```

@@

```{r}
multipleMediatorFit <- sem(
  multipleMediatorModel,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  se = "bootstrap",
  bootstrap = 1000, # generally use 10,000 bootstrap draws; this example uses 1,000 for speed
  parallel = "multicore", # parallelization for speed: use "multicore" for Mac/Linux; "snow" for PC
  iseed = 52242, # for reproducibility
  missing = "ML",
  estimator = "ML",
  fixed.x = FALSE)
```
